Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-15 PAPER.tex
Wording in descriptions of Pout regimes.

{\bf Small injection:}
%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. 
%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples. Output values are gaussian distributed around zero, spanning a range of values set by the injection level. This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below). In fact, for the unweighted case, the cross term is well modeled by $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}=\sqrt{p_e}\sqrt{p_x}$ %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
be neglected as many orders of magnitude smaller. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green). Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e. the black and green curves agree). We again see that the cross-terms behave as noise at large injections in the empirical inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.

{\bf In between:}
When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
the cross-terms have nearly the same amplitude, but with a negative sign. The sum of the two is substantially lower and therefore drives down the $P_{\rm out}$ estimator (black). We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level. Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.

>>>>

{\bf Small injection:}
%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. 
%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples. Output values are gaussian distributed around zero, spanning a range of values set by the injection level. This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below). In fact, for the unweighted case, the cross term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$. %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal is much larger than the measured power spectrum, the data-only components can 
be neglected as many orders of magnitude smaller. This regime is somewhat academic given that, in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal.  However it is useful as a check of our system in a relatively simple case.   As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term. Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output. We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean). This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$. The cross correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.

{\bf In between:}
When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
the cross-term has nearly the same amplitude, but with a negative sign. As explained below, this negativity is the result of cross correlating inverse covariance weighted things.  This negative component drives down the $P_{\rm out}$ estimator (black). We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level. Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.
